Community Analysis

### 2022-07-15 R/08-community-analysis.Rmd
add dbrda and start updating da

@@

@@

all_taxa <-
  all_taxa %>%
	mutate(Genus = str_replace(Genus, "(.*)", "*\\1*"),
	       Genus = str_replace(Genus, "\\*(.*)_unclassified\\*",
				    "Unclassified *\\1*"))
all_taxa$Genus[all_taxa$Genus == "Unclassified *0319-6G20*"] <- "Uncultured Genus 0319-6G20"
all_taxa$Genus[all_taxa$Genus == "Unclassified *Chloroplast*"] <- "Chloroplast"
all_taxa$Genus[all_taxa$Genus == "Unclassified *Armatimonadales*"] <- "Unclassified Armatimonadales"
all_taxa$Genus[all_taxa$Genus == "Unclassified *Gammaproteobacteria*"] <- "Unclassified Gammaproteobacteria"
all_taxa$Genus[all_taxa$Genus == "Unclassified *Kapabacteriales*"] <- "Unclassified Kapabacteriales"

>>>>

if(file.exists("Output/ancom_out_genus.rds")) {
  out <- 
    readRDS("Output/ancom_out_genus.rds")
} else {
  # Run Ancom
  out = ancom(phyloseq = aes_ps,  
              p_adj_method = "BH",
              prv_cut = 0.1, 
              lib_cut = 0, 
              main_var = "treat",
              rand_formula = NULL, 
              lme_control = NULL,
              struc_zero = TRUE, 
              neg_lb = FALSE, 
              alpha = 0.05, 
              n_cl = 1)  
  out %>% 
    saveRDS("Output/ancom_out_genus.rds")
}

@@

if(file.exists("Output/aldex_x_all_genus.rds")) {
  x.all <- 
    readRDS("Output/aldex_x_all_genus.rds")
} else {
  x.all <- aldex(otu_table, 
                 conds, mc.samples=1000, test="t", effect=TRUE,
                 include.sample.summary=FALSE, denom="all", verbose=FALSE, paired.test=FALSE)
  x.all %>% 
    saveRDS("Output/aldex_x_all_genus.rds")
}

@@

all_taxa <-
  all_taxa %>%
	mutate(Genus = str_replace(Genus, "(.*)", "*\\1*"),
	       Genus = str_replace(Genus, "\\*(.*)_unclassified\\*",
				    "Unclassified *\\1*"))
# all_taxa$Genus[all_taxa$Genus == "Unclassified *0319-6G20*"] <- "Uncultured Genus 0319-6G20"
# all_taxa$Genus[all_taxa$Genus == "Unclassified *Chloroplast*"] <- "Chloroplast"
# all_taxa$Genus[all_taxa$Genus == "Unclassified *Armatimonadales*"] <- "Unclassified Armatimonadales"
# all_taxa$Genus[all_taxa$Genus == "Unclassified *Gammaproteobacteria*"] <- "Unclassified Gammaproteobacteria"
# all_taxa$Genus[all_taxa$Genus == "Unclassified *Kapabacteriales*"] <- "Unclassified Kapabacteriales"
